\vspace{-2.25cm} Multimodal Abnormity-Aware Model\\for Ocular Disease Diagnosis

### 2024-08-29 Paper/Paper.tex
add bib ref.

	The Abnormity Models also contain 2 submodels: the OCT Model and the Fundus Model, which classify OCT and fundus abnormities, respectively. Both of the submodels leverage CNNs with modified final fully-connected (FC) layers. We compare the performances of 4 commonly used CNNs, ResNet152, ResNet50, ResNet18 and VGG16, and choose the best one for each submodel. The final FC layer in each CNN is modified so that the size of its output vector is equal to the number of OCT or fundus abnormities. In order to normalize the output vector, we perform the softmax operation. Each submodel outputs a probability vector for all the abnormities.

@@

	For OCT abnormities with less than 1000 images, we use Cycle-GAN to generate new images. We train a Cycle-GAN network to interconvert healthy and abnormity images, take out the generator that converts healthy to abnormity images, and use it to generate new abnormity images. We go through all generated images and adopt those that clearly display only the abnormity of interest. The adoption rates are shown in Table~\ref{tb:cycleGAN_number}. Fundus images are not generated using Cycle-GAN because generated fundus images are too blurry; in addition, fundus abnormities are usually less salient than OCT ones and cannot be properly learned by Cycle-GAN, given that we only have a small number of fundus images.

>>>>

	The Abnormity Models also contain 2 submodels: the OCT Model and the Fundus Model, which classify OCT and fundus abnormities, respectively. Both of the submodels leverage CNNs with modified final fully-connected (FC) layers. We compare the performances of 4 commonly used CNNs, ResNet152, ResNet50, ResNet18\autocite{He_Zhang_Ren_Sun_2016} and VGG16\autocite{Simonyan_Zisserman_2015}, and choose the best one for each submodel. The final FC layer in each CNN is modified so that the size of its output vector is equal to the number of OCT or fundus abnormities. In order to normalize the output vector, we perform the softmax operation. Each submodel outputs a probability vector for all the abnormities.

@@

	For OCT abnormities with less than 1000 images, we use Cycle-GAN\autocite{Zhu_Park_Isola_Efros_2020} to generate new images. We train a Cycle-GAN network to interconvert healthy and abnormity images, take out the generator that converts healthy to abnormity images, and use it to generate new abnormity images. We go through all generated images and adopt those that clearly display only the abnormity of interest. The adoption rates are shown in Table~\ref{tb:cycleGAN_number}. Fundus images are not generated using Cycle-GAN because generated fundus images are too blurry; in addition, fundus abnormities are usually less salient than OCT ones and cannot be properly learned by Cycle-GAN, given that we only have a small number of fundus images.
